Two-Phase Commit Using Blockchain

### 2022-06-04 paper/paper.tex
Link reference and remove other duplicated line.
Update appendix and references titles.
Add consistent Get and Put syntax.

As described in \ref{}, the coordinator does not need to persist any information to disk as all voting information is stored in the blockchain and all other information (e.g. list of cohorts involved in the transaction) is also known by the client.

@@

The \texttt{PrepareTransactionRequest()} contains a \texttt{transaction\_id}, a list of operations of the sub-transaction and the vote timeout time, after which the blockchain will not accept votes. When a cohort receives a \texttt{PrepareTransaction()} request from the coordinator, it takes these steps: 
\begin{enumerate}
  \item Start a new thread in the thread pool.
  \item Create a \texttt{DatabaseAdapter} object.
  \item Start a transaction with \texttt{DatabaseAdapter:: Begin()}.
  \item Acquire the relevant locks for the sub-transaction.
  \item Execute a series of requested \texttt{Put} or \texttt{Get} operations in the sub-transaction. 
  \item If any operation is reported invalid by the database or locks cannot be acquired in time, the cohort will send an \texttt{ABORT} ballot to the blockchain via \texttt{BlockchainAdapter::Vote()}.
  \item If all operations succeed, it will store the retrieved Get values in an in-memory hashmap as well as persistently on disk keyed by the \texttt{transaction\_id} to prepare for future \texttt{GetTransactionResult()} calls.
  \item Set a timer based on the input vote timeout time.
  \item If the timer reaches the vote timeout time, it will send a request \texttt{BlockchainAdapter::\\GetVotingDecision(transaction\_id)} to the blockchain. 
    \begin{enumerate}
      \item If the blockchain states that the transaction should be committed, it will call \texttt{DatabaseAdapter::Commit()} and release any acquired locks.
  \item If the blockchain states that the transaction should be aborted, it will call \texttt{DatabaseAdapter::Abort()} and release any acquired locks.
  \end{enumerate}
\end{enumerate}

@@

\begin{enumerate}
  \item The client composes a transaction request and passes it to the coordinator through \texttt{CommitAomticTransaction()}. The coordinator returns a transaction ID for the client to look up the transaction result later.
  \item The coordinator asks the blockchain to trace votes for the new transaction through \texttt{StartVoting()}.
  \item The coordinator decomposes the transaction into sub-transactions and distributes them to the corresponding cohort through \texttt{PrepareTransaction()}.
  \item Each cohort executes a sub-transaction by acquiring locks and forwarding the operations to the database up to the point before Commit(). The cohort writes an entry to the redo log to recover in case it crashes. Additionally, the cohort writes the \texttt{GET} operation results to disk for faster responses after a crash and recovery.
  \item The cohort votes to the blockchain through \texttt{Vote()} indicating that it wants to commit or abort the transaction.
  \item The cohort waits until the expected transaction vote timeout time and gets the voting decision from the blockchain through \texttt{GetVotingDecision()}.
  \item If the voting decision is to commit the transaction, the cohort commits the sub-transaction onto the database and releases any acquired locks; otherwise, it aborts the sub-transaction in the database and releases any acquired locks.
  \item (Independent of the previous steps) The client waits until the vote timeout time and requests the transaction result from the coordinator through \texttt{GetTransactionResult()}, using the transaction ID given in step 1.
  \item The coordinator gets (1) the voting decision of the inquiry transaction from the blockchain through \texttt{GetTransactionResult()} and (2) the \texttt{GET} operation results from each cohort.
\end{enumerate}

@@

\subsubsection{Distributed coordinator}
Currently the coordinator is stateless, so it is easy to add new coordinator servers, as long as each one handles a disjoint set of transactions. However, if a coordinator crashes, then clients cannot ask other coordinators for the Get responses of a transaction, since those coordinators will not know how to find the cohorts for the transaction. As part of a future effort, we could have the coordinators send each other the cohorts for each transaction so they can respond to client requests even if the original coordinator for that request crashes.

\section{Reference}

\section{Appendix} \label{appendix}
\begin{table}[hbtp]
  \centering
  \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
  \label{table:cost}
  \begin{tabular}{|l|c|c|c|}
    \hline
          & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          \hline
    StartVoting &73441 &0.000073441 & 0.143\\
    \hline
    Vote 1 &56451	&0.000056451 &0.110\\
    \hline
    Vote 2 &39513 &0.000039513 &0.077\\
    \hline
  \end{tabular}
\end{table}
\end{document}
\endinput

>>>>

@@

The \texttt{PrepareTransactionRequest()} contains a \texttt{transaction\_id}, a list of operations of the sub-transaction and the vote timeout time, after which the blockchain will not accept votes. When a cohort receives a \texttt{PrepareTransaction()} request from the coordinator, it takes these steps: 
\begin{enumerate}
  \item Start a new thread in the thread pool.
  \item Create a \texttt{DatabaseAdapter} object.
  \item Start a transaction with \texttt{DatabaseAdapter:: Begin()}.
  \item Acquire the relevant locks for the sub-transaction.
  \item Execute a series of requested \texttt{Put} or \texttt{Get} operations in the sub-transaction. 
  \item If any operation is reported invalid by the database or locks cannot be acquired in time, the cohort will send an \texttt{ABORT} ballot to the blockchain via \texttt{BlockchainAdapter::Vote()}.
  \item If all operations succeed, it will store the retrieved \texttt{Get} values in an in-memory hashmap as well as persistently on disk keyed by the \texttt{transaction\_id} to prepare for future \texttt{GetTransactionResult()} calls.
  \item Set a timer based on the input vote timeout time.
  \item If the timer reaches the vote timeout time, it will send a request \texttt{BlockchainAdapter::\\GetVotingDecision(transaction\_id)} to the blockchain. 
    \begin{enumerate}
      \item If the blockchain states that the transaction should be committed, it will call \texttt{DatabaseAdapter::Commit()} and release any acquired locks.
  \item If the blockchain states that the transaction should be aborted, it will call \texttt{DatabaseAdapter::Abort()} and release any acquired locks.
  \end{enumerate}
\end{enumerate}

@@

\begin{enumerate}
  \item The client composes a transaction request and passes it to the coordinator through \texttt{CommitAomticTransaction()}. The coordinator returns a transaction ID for the client to look up the transaction result later.
  \item The coordinator asks the blockchain to trace votes for the new transaction through \texttt{StartVoting()}.
  \item The coordinator decomposes the transaction into sub-transactions and distributes them to the corresponding cohort through \texttt{PrepareTransaction()}.
  \item Each cohort executes a sub-transaction by acquiring locks and forwarding the operations to the database up to the point before Commit(). The cohort writes an entry to the redo log to recover in case it crashes. Additionally, the cohort writes the \texttt{Get} operation results to disk for faster responses after a crash and recovery.
  \item The cohort votes to the blockchain through \texttt{Vote()} indicating that it wants to commit or abort the transaction.
  \item The cohort waits until the expected transaction vote timeout time and gets the voting decision from the blockchain through \texttt{GetVotingDecision()}.
  \item If the voting decision is to commit the transaction, the cohort commits the sub-transaction onto the database and releases any acquired locks; otherwise, it aborts the sub-transaction in the database and releases any acquired locks.
  \item (Independent of the previous steps) The client waits until the vote timeout time and requests the transaction result from the coordinator through \texttt{GetTransactionResult()}, using the transaction ID given in step 1.
  \item The coordinator gets (1) the voting decision of the inquiry transaction from the blockchain through \texttt{GetTransactionResult()} and (2) the \texttt{Get} operation results from each cohort.
\end{enumerate}

@@

\subsubsection{Distributed coordinator}
Currently the coordinator is stateless, so it is easy to add new coordinator servers, as long as each one handles a disjoint set of transactions. However, if a coordinator crashes, then clients cannot ask other coordinators for the \texttt{Get} responses of a transaction, since those coordinators will not know how to find the cohorts for the transaction. As part of a future effort, we could have the coordinators send each other the cohorts for each transaction so they can respond to client requests even if the original coordinator for that request crashes.

\bibliographystyle{plain}
\bibliography{references}

\appendix
\label{appendix}
\begin{table}[hbtp]
  \centering
  \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
  \label{table:cost}
  \begin{tabular}{|l|c|c|c|}
    \hline
          & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          \hline
    StartVoting &73441 &0.000073441 & 0.143\\
    \hline
    Vote 1 &56451	&0.000056451 &0.110\\
    \hline
    Vote 2 &39513 &0.000039513 &0.077\\
    \hline
  \end{tabular}
\end{table}
\end{document}
\endinput
